---
title: "Linear Regression"
author: "Nurmatov Salim"
date: "30 11 2020"
output: html_document
---


###   Load  dataset, and remove all   duplicates (or more formally only females records should be in the dataset) that does not have any duplicate rows of data (done in homework 3.2). 
```{r}
zeta <- read.csv("D:/zeta.csv", header = TRUE)
my_data <- subset(zeta, !ave(meanhouseholdincome, FUN = duplicated))

```

###   Remove the columns zcta and sex from the imported table.
```{r}
my_new_data <- subset(my_data, select = -c(X, zcta))
```

###   Remove outliers by creating subsets of the original data so that: 
```{r}
my_second_data <- subset(my_new_data, (meaneducation > 8 & meaneducation < 18 & meanhouseholdincome > 1000 & meanhouseholdincome < 200000 & meanage > 20 & meanage < 60 & meanemployment > 0 & meanemployment < 3))
```
###Second way (same)
```{r}
my_second_data <- my_new_data[(my_new_data$meaneducation > 8 & my_new_data$meaneducation < 18),]
```

###   Create a variable called log_income = log10(meanhouseholdincome).
```{r}
log_income = log10(my_second_data$meanhouseholdincome)###variable
my_second_data$log_income <- my_second_data$meanhouseholdincome
my_second_data$log_income <- log10(my_second_data$log_income)
```

###   Rename the columns meanage, meaneducation and meanemployment as age, education and employment, respectively.
```{r}
names(my_second_data)[names(my_second_data) == "meanage"] <- "age"
names(my_second_data)[names(my_second_data) == "meaneducation"] <- "education"
names(my_second_data)[names(my_second_data) == "meanemployment"] <- "employment"
```
#   Linear Regression Analysis

###a.      We will be analyzing this data with income as the dependent variable and the other columns as independent variables.  Create a scatter plot showing the effect age has on log_income and paste it here.  Do you see any linear relationship between the two variables?
```{r}
library(ggplot2)
ggplot(my_second_data, aes(x = age, y = log_income)) + geom_point(alpha = 0.1)
```

###b.      Create a linear regression model between log_income and age.  What is the interpretation of the t-value? What kind of t-value would indicate a significant coefficient?
```{r}
Lm_1 <- lm(data = my_second_data, log_income~age)
summary(Lm_1)
```

```{r}
plot(fitted(Lm_1), resid(Lm_1), xlab = "age", ylab = "log_income")
```


```{r}
Lm_1 <- lm(data = my_second_data, log_income~age)
summary(Lm_1)
```
```{r}
plot(fitted(Lm_1), log_income, xlab = "pre_income", ylab = "true_income")
abline(a = 0, b = 1, col = "red")
```
```{r}
plot(my_second_data$age, log_income, xlab = "age", ylab = "log10(income)")
lines(my_second_data$age, predict(Lm_1), col = "red")
```



###c.       What is the interpretation of the R-squared value?  What kind of R-squared value would indicate a good fit?

###d.      What is the interpretation of the F-statistic?  What kind of F-statistic indicates a strong linear regression model?

###e.      View a detailed summary of the previous model.  What is the R-squared value?  Does this suggest that the model is a good fit? Why?

###f.        Create a scatter plot showing the effect education has on log_income.  Do you see any linear relationship between the two variables?
```{r}
library(ggplot2)
ggplot(my_second_data, aes(x = education, y = log_income)) + geom_point(alpha = 0.1)

```

###g.      Analyze a detailed summary of a linear regression model between log_income and education.  What is the R-squared value?  Is the model a good fit?  Is it better than the previous model?
```{r}
lm_2 <- lm(data = my_second_data, log_income~education)
summary(lm_2)
```

###h.      Analyze a detailed summary of a linear regression model between the dependent variable log_income, and the independent variables age, education, and employment.  Is this model a good fit?  Why?  What conclusions can be made about the different independent variables?
```{r}
lm_3 <- lm(data = my_second_data, log_income~age+education+employment)
summary(lm_3)
```

###i.        Based on the coefficients of the multiple regression model, by what percentage would income increase/decrease for every unit of education completed, while all other independent variables remained constant?
```{r}
coefficients(lm_3)
```

###j.        Create a graph that contains a y = x line and uses the multiple regression model to plot the predicted data points against the actual data points of the training set. 
```{r}
plot(fitted(lm_3), log_income, xlab = "pre_income", ylab = "log_income")
abline(a = 0, b = 1, col = "red")
```

